---
title: "elk.data"
author: "Kassie McCurrach"
date: "2026-09-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##**Loading Packages**
```{r}
library(rstatix)
library(mgcv)
library(mgcViz)
library(ggplot2)
library(DHARMa)
library(fitdistrplus)
library(gamlss)
library(goft)
library(tidyverse)
```

##**Loading Data
```{r}
# I added a data folder to your project with 
# the two current csv files. These might eventually
# become too large to share via GitHub, but this
# will work for now and allow us to collaborate better.
data <- read_csv("data/ASCCA_2026_June_August_tag_report.csv")

```


##**Cleaning Data
```{r}
data.clean <- data %>%
  select(location, image_date_time, species_common_name) %>%
  filter(!str_starts(location, "1")) %>%
  filter(species_common_name == "Elk (wapiti)") %>%
  mutate(month = month(image_date_time), day = day(image_date_time), hour = hour(image_date_time), minute = minute(image_date_time)) %>%
  group_by(location)

```


##**Creating Function To Caclulate Time Difference Between Photos
```{r}
# I'm making the argument more generic ("dt") so 
# you can specify the data you want to use, which # will allow you to use it more generally. Within 
# the function, "dt" can be anything you want.
calc_difftime <- function(dt) {
  # I removed the num_vec <- c() because I don't 
  # think it's needed
  new.elk.data <- tibble()
  for(i in unique(dt$location)) {
    # Here data.clean is replaced with dt, which
    # you will specify when running the function.
    cam_location <- dt %>% 
     filter(location == i)
    time_diffs <- tibble(time_diff = NA)
    for(j in 1:nrow(cam_location)){
      if(j == 1) {
      time_diffs[j, ]$time_diff <- NA}
      if(j>1) {
      time_diffs [j, ]$time_diff <- 
        cam_location[j, ]$image_date_time - 
        cam_location[j-1, ]$image_date_time
      }
    }
    # I'm making a new column, "location", which
    # gets filled with i (the location)
    time_diffs$location <- i
    # Then I'm binding together the empty tibble
    # (new.elk.data) with the time_diffs you 
    # generated.
    new.elk.data <- bind_rows(new.elk.data, time_diffs)
  }
  # Now the function should return a tibble with
  # all of the time diffs labelled by location.
return(new.elk.data)
  }

# This should now work the way you want it to.
# This is a great function that will calculate
# the time differences for any new tibble as we 
# add data in the future. Great job!
calc_difftime(dt = data.clean)
 
  
```
Making a Function:
add3 <- function(input) input + 3
add3(3)


for(i in unique(cam_data$camera_id)) 
cam_new <- cam_data %>% (filter == camera_ID == i)
camdiff <- tibble(cam =i, diff_time = cam_new[i]$datetime - ) this will isolate each species or camera location
calc_difftime <- function(data, camera)

https://purrr.tidyverse.org/articles/purrr.html (package to do the last part of the code that levi sent)


https://www.r-bloggers.com/2015/07/a-tutorial-on-loops-in-r-usage-and-alternatives/ (use to complete last part) (loops would be the easiest way to complete the time difference between adjacent rows) START HERE

https://r4ds.had.co.nz/functions.html (how to make your own functions)